Emittance preservation of an electron beam in a loaded quasi-linear plasma wakefield

### 2017-10-11 Tex/Paper.tex
Some text changes to offset paragraph

Equation~(\ref{EQ:Matched}) yields a transverse size $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, which is narrow compared
to the drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$, based
on earlier beam loading studies~\cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
\emph{base case}. Figure~\ref{Fig:PlasmaDenTWake} shows the two beams from a QuickPIC simulation of the initial time
step, for the base case parameters; the proton beam in blue, the trailing electron beam in red, and the plasma electron
density in grey.

@@

Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x}$, but
with a cost in the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows the
correlation between this ratio for a range of offsets up to $4\cdot\sigma_{x}$. The effect on the head of the beam shown
in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament} increase with larger offsets causing the section of the beam
being defocused to extend backwards to the point where the witness beam wakefields are no longer non-linear as the
offset approaches $4\cdot\sigma_{x}$.

>>>>

Equation~(\ref{EQ:Matched}) yields a transverse size $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, which is narrow compared
to the drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$ based
on earlier beam loading studies~\cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
\emph{base case}. Figure~\ref{Fig:PlasmaDenTWake} shows the two beams from a QuickPIC simulation of the initial time
step, for the base case parameters; the proton beam in blue, the trailing electron beam in red, and the plasma electron
density in grey.

@@

Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x}$, but
with a cost in the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows the
correlation between this ratio for a range of offsets up to $3.2\cdot\sigma_{x}$. The effect on the head of the beam,
shown in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament}, increases with larger offsets causing the section of the
beam being defocused to extend backwards to the point where the witness beam wakefields are no longer in the blow-out
regime. At around $3\cdot\sigma_{x}$ emittance is no longer preserved at all.
